Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-03-29 W13report.tex
Cellsize discussion.

\begin{figure}
\centering{\includegraphics[width=1.0\textwidth]{figures/cellsize.eps}} \\
\caption{False detections with cell size {\bf WRITE ME}
}
\label{cellsize}
\end{figure}

>>>>

\begin{figure}
\centering{\includegraphics[width=1.0\textwidth]{figures/cellsize.eps}} \\
\caption{We show the number of false detections ({\it left}) and {\tt
    KernelCandidates} used in the spatial kernel fit ({\it right}) as
  a function of {\tt SpatialCell} size.  Increasing the cell size,
  while keep all other things equal, effectively decreases the number
  of constraints on the spatial model.  As shown on the left, the
  prefiltered data ({\it dashed} lines) have a less strong dependence
  on the number of constraints compared to the postfiltered data ({\it
    solid} lines).  The prefiltered data show essentially similar
  quality when using 300 vs. 600 {\tt KernelCandidates}, while in the
  postfiltered data the number of false positives increases by nearly
  a factor of 2 (from cellsize 128 to 384).  }
\label{cellsize}
\end{figure}
